The title

### 2022-11-02 paper/manuscript.Rmd
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music.

We found that expert pianists did not modulate their tempo depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo is not employed specifically for teaching because tempo itself is relevant to neither articulation nor dynamics. In music performance, it is possible that changing tempo might give another interpretation of music (e.g., expressive timing).

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to replicate the performances of students with high skills. On the other hand, the recordings where none of the two techniques was implemented were supposed to replicate the performances of students with low skills. The recordings where either of the two techniques was implemented but the other was missing were equivalent to the performances of students with intermediate skills.

We found that expert pianists did not modulate their tempo (IOIs) depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo was not employed specifically for teaching because tempo itself was relevant to neither articulation nor dynamics. Especially in music performance, it may not be an effective strategy to perform slowly as changing tempo might give another interpretation of music (e.g., expressive timing).

### 2022-11-02 paper/manuscript.tex
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music.

We found that expert pianists did not modulate their tempo depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo is not employed specifically for teaching because tempo itself is relevant to neither articulation nor dynamics. In music performance, it is possible that changing tempo might give another interpretation of music (e.g., expressive timing).

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to replicate the performances of students with high skills. On the other hand, the recordings where none of the two techniques was implemented were supposed to replicate the performances of students with low skills. The recordings where either of the two techniques was implemented but the other was missing were equivalent to the performances of students with intermediate skills.

We found that expert pianists did not modulate their tempo depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo is not employed specifically for teaching because tempo itself is relevant to neither articulation nor dynamics. Especially in music performance, it may not be an effective strategy to perform slowly as changing tempo might give another interpretation of music (e.g., expressive timing).
